\input cwebmac

% jafco

\nocon % omit table of contents
\datethis % print date on listing


\N{1}{1}Introduction. This is the firmware portion of Jaw and Fire control.

This will facilitate two actions: opening the jaw to release the floating
object and light the target on fire.

The jaw will close by return-spring so the action will to open it.

Fire is a  sequence of opening the jaw, releasing the butane and firing the
ignitor.

place-holder code below
==========================

Extensive use was made of the datasheet, Atmel ``Atmel ATtiny25, ATtiny45,
ATtiny85 Datasheet'' Rev. 2586Q–AVR–08/2013 (Tue 06 Aug 2013 03:19:12 PM
EDT)
and ``AVR130: Setup and Use the AVR Timers'' Rev. 2505A–AVR–02/02.
\Y\B\X4:Include\X\6
\X5:Types\X\6
\X6:Prototypes\X\6
\X7:Global variables\X\par
\fi

\M{2}\PB{\.{"F\_CPU"}} is used to convey the Trinket clock rate.
\Y\B\4\D$\.{F\_CPU}$ \5
\T{8000000\$U\$L}\par
\fi

\M{3}Here are some Boolean definitions that are used.
\Y\B\4\D$\.{ON}$ \5
\T{1}\par
\B\4\D$\.{OFF}$ \5
\T{0}\par
\B\4\D$\.{OPEN}$ \5
\T{1}\par
\B\4\D$\.{CLOSE}$ \5
\T{0}\par
\B\4\D$\.{SET}$ \5
\T{1}\par
\B\4\D$\.{CLEAR}$ \5
\T{0}\par
\fi

\M{4}\B\X4:Include\X${}\E{}$\6
\8\#\&{include} \.{<avr/io.h>}\SHC{ need some port access }\6
\8\#\&{include} \.{<util/delay.h>}\SHC{ need to delay }\6
\8\#\&{include} \.{<avr/interrupt.h>}\SHC{ have need of an interrupt }\6
\8\#\&{include} \.{<avr/sleep.h>}\SHC{ have need of sleep }\6
\8\#\&{include} \.{<stdlib.h>}\6
\8\#\&{include} \.{<stdint.h>}\par
\U1.\fi

\M{5}Here is a structure to keep track of the state of things.

\Y\B\4\X5:Types\X${}\E{}$\6
\&{typedef} \&{struct} ${}\{{}$\1\6
\\{uint8\_t}\\{count};\2\6
${}\}{}$ \&{statestruct};\par
\U1.\fi

\M{6}\B\X6:Prototypes\X${}\E{}$\6
\&{void} \\{jawcntl}(\\{uint8\_t}\\{state});\SHC{ Jaw open and close }\6
\&{void} \\{fuelcntl}(\\{uint8\_t}\\{state});\SHC{ Fuel on and off }\6
\&{void} \\{igncntl}(\\{uint8\_t}\\{state});\SHC{ on and off }\6
\&{void} \\{fireseq}(\&{statestruct} ${}{*});{}$\6
\&{void} \\{releaseseq}(\&{statestruct} ${}{*}){}$;\par
\U1.\fi

\M{7}
My lone global variable is a function pointer.
This lets me pass arguments to the actual interrupt handlers.
This pointer gets the appropriate function attached by one of the \PB{%
\.{"ISR()"}}
functions.

\Y\B\4\X7:Global variables\X${}\E{}$\6
$\&{void}({*}\\{handleirq}){}$(\&{statestruct} ${}{*})\K\NULL{}$;\par
\U1.\fi

\M{8}
Here is \PB{\\{main}(\,)}.
\Y\B\&{int} \\{main}(\&{void})\1\1 $\{{}$\Y\par
\fi

\M{9}The prescaler is set to clk/16484 by \PB{$\X27:Initialize the timer\X$}.
With \PB{\.{"F\_CPU"}} at 8~MHz, the math goes: $\lfloor{0.5 seconds \times (8 %
\times 10^6 \over 16384}\rfloor = 244$.
Then, the remainder is $256-244 = 12$, thus leaving 244 counts or about 500 ms
until time-out, unless it's reset.

\Y\B\&{statestruct} \\{s\_state}; \X23:Initialize pin inputs\X\X22:Initialize
pin outputs\X\par
\fi

\M{10}
\Y\B\\{jawcntl}(\.{CLOSE});\C{ PB0 }\6
\\{fuelcntl}(\.{OFF});\C{ PB1 }\6
\\{igncntl}(\.{OFF});\C{ PB2 }\par
\fi

\M{11}
Here the timer is setup.
\Y\B\X27:Initialize the timer\X\par
\fi

\M{12}
Of course, any interrupt function requires that bit ``Global Interrupt Enable''
is set; usually done through calling sei().
\Y\B\\{sei}(\,);\par
\fi

\M{13}
Rather than burning loops, waiting 16~ms for something to happen,
the ``sleep'' mode is used.
The specific type of sleep is `idle'.
In idle, execution stops but timers continue.
Interrupts are used to wake it.
\Y\B\X28:Configure to wake upon interrupt\X\par
\fi

\M{14}
This is the loop that does the work.
It should spend most of its time in \PB{\\{sleep\_mode}},
comming out at each interrupt event.

\Y\B\&{for} ( ;  ; \,) $\{{}$\Y\par
\fi

\M{15}
Now we wait in ``idle'' for any interrupt event.
\Y\B\\{sleep\_mode}(\,);\par
\fi

\M{16}
If execution arrives here, some interrupt has been detected.
\Y\B\&{if} ${}(\\{handleirq}\I\NULL{}$)\SHC{ not sure why it would be, but to
be safe }\6
${}\{{}$\1\7
${}\\{handleirq}({\AND}\\{s\_state}){}$;\SHC{ process the irq through it's
function }\6
${}\\{handleirq}\K\NULL{}$;\SHC{ reset so that the action cannot be repeated }\6
\4${}\}{}$\SHC{ end if handleirq }\2\7
$\}{}$\SHC{ end for }\7
\&{return} \T{0};\SHC{ it's the right thing to do! }\7
$\}{}$\SHC{ end main() }\par
\fi

\N{1}{17}Interrupt Handling.

\Y\B\&{void} \\{releaseseq}(\&{statestruct} ${}{*}\\{s\_now}){}$\1\1\2\2\6
${}\{\,\}{}$\par
\fi

\M{18}


\Y\B\&{void} \\{fireseq}(\&{statestruct} ${}{*}\\{s\_now}){}$\1\1\2\2\6
${}\{\,\}{}$\par
\fi

\M{19}The ISRs are pretty skimpy as they are only used to point \PB{%
\\{handleirq}(\,)} to
the correct function.
The need for global variables is minimized.


This is the vector for the main timer.
When this overflows it generally means the ASE has been off for as long as it
took \PB{\.{TCINT1}} to overflow from it's start at \PB{\.{NOWAVETIME}}.
\Y\B\C{ Timer ISR }\6
\.{ISR}(\\{TIMER1\_OVF\_vect})\1\1\2\2\6
${}\{{}$\1\6
${}\\{handleirq}\K\NULL;{}$\6
\4${}\}{}$\2\par
\fi

\M{20}
This vector responds to the jaw input at pin PB4 or PB4.
\Y\B\C{ Clear Button ISR }\6
\.{ISR}(\\{PCINT0\_vect})\1\1\2\2\6
${}\{{}$\1\6
${}\\{handleirq}\K{\AND}\\{releaseseq};{}$\6
\4${}\}{}$\2\par
\fi

\N{1}{21}These are the supporting routines, procedures and configuration
blocks.


Here is the block that sets-up the digital I/O pins.
\fi

\M{22}\B\X22:Initialize pin outputs\X${}\E{}$\6
${}\{{}$\C{ set the jaw port direction }\1\6
${}\.{DDRB}\MRL{{\OR}{\K}}(\T{1}\LL\.{DDB0}){}$;\C{ set the fuel port direction
}\6
${}\.{DDRB}\MRL{{\OR}{\K}}(\T{1}\LL\.{DDB1}){}$;\C{ set the ignition port
direction }\6
${}\.{DDRB}\MRL{{\OR}{\K}}(\T{1}\LL\.{DDB2});{}$\6
\4${}\}{}$\2\par
\U9.\fi

\M{23}\B\X23:Initialize pin inputs\X${}\E{}$\6
${}\{{}$\C{ set the jaw input pull-up }\1\6
${}\.{PORTB}\MRL{{\OR}{\K}}(\T{1}\LL\.{PORTB3}){}$;\C{ set the fire input
pull-up }\6
${}\.{PORTB}\MRL{{\OR}{\K}}(\T{1}\LL\.{PORTB4}){}$;\C{ enable  change interrupt
for jaw input }\6
${}\.{PCMSK}\MRL{{\OR}{\K}}(\T{1}\LL\.{PCINT3}){}$;\C{ enable  change interrupt
for fire input }\6
${}\.{PCMSK}\MRL{{\OR}{\K}}(\T{1}\LL\.{PCINT4}){}$;\C{ General interrupt Mask
register for clear-button}\6
${}\.{GIMSK}\MRL{{\OR}{\K}}(\T{1}\LL\.{PCIE});{}$\6
\4${}\}{}$\2\par
\U9.\fi

\M{24}
Here is a simple function to operate the jaw.
\Y\B\&{void} \\{jawcntl}(\\{uint8\_t}\\{state})\1\1\2\2\6
${}\{{}$\1\6
${}\.{PORTB}\K\\{state}\?\.{PORTB}\OR(\T{1}\LL\.{PORTB0}):\.{PORTB}\AND\CM(%
\T{1}\LL\.{PORTB0});{}$\6
\4${}\}{}$\2\par
\fi

\M{25}
Here is a simple function to operate the fuel.
\Y\B\&{void} \\{fuelcntl}(\\{uint8\_t}\\{state})\1\1\2\2\6
${}\{{}$\1\6
${}\.{PORTB}\K\\{state}\?\.{PORTB}\OR(\T{1}\LL\.{PORTB1}):\.{PORTB}\AND\CM(%
\T{1}\LL\.{PORTB1});{}$\6
\4${}\}{}$\2\par
\fi

\M{26}
Here is a simple function to operate the ignition.
\Y\B\&{void} \\{igncntl}(\\{uint8\_t}\\{state})\1\1\2\2\6
${}\{{}$\1\6
${}\.{PORTB}\K\\{state}\?\.{PORTB}\OR(\T{1}\LL\.{PORTB2}):\.{PORTB}\AND\CM(%
\T{1}\LL\.{PORTB2});{}$\6
\4${}\}{}$\2\par
\fi

\M{27}
A very long prescale of 16384 counts is set by setting certain bits in \PB{%
\.{TCCR1}}.

\Y\B\4\X27:Initialize the timer\X${}\E{}$\6
${}\{{}$\1\6
${}\.{TCCR1}\K((\T{1}\LL\.{CS10})\OR(\T{1}\LL\.{CS11})\OR(\T{1}\LL\.{CS12})\OR(%
\T{1}\LL\.{CS13})){}$;\SHC{Prescale }\6
${}\.{TIMSK}\MRL{{\OR}{\K}}(\T{1}\LL\.{TOIE1}){}$;\C{ Timer 1 f\_overflow
interrupt enable }\6
\4${}\}{}$\2\par
\Q9.
\U11.\fi

\M{28}
Setting these bits configure sleep\_mode() to go to ``idle''.
Idle allows the counters and comparator to continue during sleep.

\Y\B\4\X28:Configure to wake upon interrupt\X${}\E{}$\6
${}\{{}$\1\6
${}\.{MCUCR}\MRL{\AND{\K}}\CM(\T{1}\LL\.{SM1});{}$\6
${}\.{MCUCR}\MRL{\AND{\K}}\CM(\T{1}\LL\.{SM0});{}$\6
\4${}\}{}$\2\par

\U13.\fi


\inx
\fin
\con
